---
title: "05052022 forest plots GENDER"
author: "Tianze Sun"
date: '2022-05-05'
output: html_document
---

##Filtering Variables: by timing GENDER
``` {r gender as moderator, echo = FALSE, warning = FALSE}
## all lifetime gender
allbygender_LT<- all %>% 
  filter(timing == "lifetime") %>%
  filter(gender != "all") %>%
  mutate(prop = round(w.cases/total,3)*100)

## all current gender
allbygender_current<- all %>% 
  filter(timing == "current") %>%
  filter(gender != "all") %>%
  mutate(prop = round(w.cases/total,3)*100) 

## all daily gender
allbygender_daily<- all %>% 
  filter(timing == "daily") %>%
  filter(gender != "all") %>%
  mutate(prop = round(w.cases/total,3)*100) 
```

##Meta analysis: LIFETIME use forest plot GENDER
```{r meta-analysis_LT: all (gender),echo = FALSE, warning = FALSE, fig.width = 10, fig.height=14}
# double arcsine transformation
ies.dat.all.gender <- escalc(xi = w.cases,
                  ni = total, 
                  data = allbygender_LT, 
                  measure = "PFT")

b.all.gender <- metaprop(event = w.cases, 
            n = total, 
            studlab = country,
            sm = "PFT", 
            data = ies.dat.all.gender, 
            method = "Inverse", 
            method.tau = "DL", 
            digits = 3,
            subgroup = gender,
            subgroup.name = "Gender")

b.all.gender

forest(b.all.gender,
       col.by = "black",
       leftcols = c("studlab","event","n", "year"),
       leftlabs = c("Country", "Lifetime use (n)", "Total participants (n)", "Data collection (year)"),
       rightcols = c("effect", "ci", "age_range"),
       rightlabs = c("Prevalence", "95% C.I.", "Age, years (range)"),
       xlab = "Prevalence of Lifetime HTP Use", smlab = "", 
       xlim = c(0,20),
       pscale = 100,
       weight.study = "random", squaresize = 0.5, 
       fixed = FALSE,
       digits = 2,
       transf= transf.ipft.hm)
```

##Meta analysis: CURRENT use forest plot GENDER
```{r meta-analysis_current: all (gender),echo = FALSE, warning = FALSE, fig.width = 10, fig.height=14}
# double arcsine transformation
ies.dat.all.gender <- escalc(xi = w.cases,
                  ni = total, 
                  data = allbygender_current, 
                  measure = "PFT")

b.all.gender <- metaprop(event = w.cases, 
            n = total, 
            studlab = country, 
            keepdata = TRUE,
            sm = "PFT", 
            data = ies.dat.all.gender, 
            method = "Inverse", 
            method.tau = "DL", 
            digits = 3,
            subgroup = gender,
            subgroup.name = "Gender")

b.all.gender

forest(b.all.gender,
       col.by = "black",
       leftcols = c("studlab","event","n", "year"),
       leftlabs = c("Country", "Current Use (n)", "Total participants (n)", "Data collection (year)"),
       rightcols = c("effect", "ci", "age_range"),
       rightlabs = c("Prevalence", "95% C.I.", "Age, years (range)"),
       xlab = "Prevalence of Current HTP Use", smlab = "", 
       xlim = c(0,20),
       pscale = 100,
       weight.study = "random", squaresize = 0.5, 
       fixed = FALSE,
       digits = 2,
       transf= transf.ipft.hm)
```

##Meta analysis: DAILY use forest plot GENDER
```{r meta-analysis_daily: all (gender),echo = FALSE, warning = FALSE, fig.width = 10, fig.height=14}
# double arcsine transformation
ies.dat.all.gender <- escalc(xi = w.cases,
                  ni = total, 
                  data = allbygender_daily, 
                  measure = "PFT")

b.all.gender <- metaprop(event = w.cases, 
            n = total, 
            studlab = country, 
            keepdata = TRUE,
            sm = "PFT", 
            data = ies.dat.all.gender, 
            method = "Inverse", 
            method.tau = "DL", 
            digits = 3,
            subgroup = gender,
            subgroup.name = "Gender")

b.all.gender

forest(b.all.gender,
       col.by = "black",
       leftcols = c("studlab","event","n", "year"),
       leftlabs = c("Country", "Daily (n)", "Total participants (n)", "Data collection (year)"),
       rightcols = c("effect", "ci", "age_range"),
       rightlabs = c("Prevalence", "95% C.I.", "Age, years (range)"),
       xlab = "Prevalence of HTP Daily Use", smlab = "", 
       xlim = c(0,20),
       pscale = 100,
       weight.study = "random", squaresize = 0.5, 
       fixed = FALSE,
       digits = 2,
       transf= transf.ipft.hm)
```

##Meta-Regression (age_group): LIFETIME use GENDER
```{r meta-regression_daily: all (Western Pacific Region),echo = FALSE, warning = FALSE, fig.width = 10, fig.height=14}
#all lifetime age_group
ies.dat.all.LT <- escalc(xi = w.cases,
                  ni = total, 
                  data = allbygender_LT, 
                  keepdata = TRUE,
                  measure = "PFT")

## random-effects model
res <- rma(yi, vi, mods = ~ gender, data=ies.dat.all.LT)
res
```

##Meta-Regression (age_group): CURRENT use GENDER
```{r meta-regression_daily: all (Western Pacific Region),echo = FALSE, warning = FALSE, fig.width = 10, fig.height=14}
#all lifetime age_group
ies.dat.all.current <- escalc(xi = w.cases,
                  ni = total, 
                  data = allbygender_current, 
                  keepdata = TRUE,
                  measure = "PFT")

## random-effects model
res <- rma(yi, vi, mods = ~ gender, data=ies.dat.all.current)
res
```

##Meta-Regression (age_group): DAILY use GENDER
```{r meta-regression_daily: all (Western Pacific Region),echo = FALSE, warning = FALSE, fig.width = 10, fig.height=14}
#all daily age_group
ies.dat.all.daily <- escalc(xi = w.cases,
                  ni = total, 
                  data = allbygender_daily, 
                  keepdata = TRUE,
                  measure = "PFT")

## random-effects model
res <- rma(yi, vi, mods = ~ gender, data=ies.dat.all.daily)
res
```

```{r gender region lifetime, echo = FALSE, warning = FALSE}

allbygender_LT_RA<- all %>% 
  filter(timing == "lifetime") %>%
  filter(gender != "all") %>%
  filter(region == "Region of the Americas") %>%
  mutate(prop = round(w.cases/total,3)*100)

allbygender_LT_ER<- all %>% 
  filter(timing == "lifetime") %>%
  filter(gender != "all") %>%
  filter(region == "European Region") %>%
  mutate(prop = round(w.cases/total,3)*100)

allbygender_LT_WPR<- all %>% 
  filter(timing == "lifetime") %>%
  filter(gender != "all") %>%
  filter(region == "Western Pacific Region") %>%
  mutate(prop = round(w.cases/total,3)*100)
```

##Meta analysis: LIFETIME use forest plot GENDER WPR
```{r meta-analysis_LT: all (gender),echo = FALSE, warning = FALSE, fig.width = 10, fig.height=14}
# double arcsine transformation
ies.dat.all.gender <- escalc(xi = w.cases,
                  ni = total, 
                  data = allbygender_LT_ER, 
                  measure = "PFT")

b.all.gender <- metaprop(event = w.cases, 
            n = total, 
            studlab = country, 
            keepdata = TRUE,
            sm = "PFT", 
            data = ies.dat.all.gender, 
            method = "Inverse", 
            method.tau = "DL", 
            digits = 3,
            subgroup = gender,
            subgroup.name = "Gender")

b.all.gender

forest(b.all.gender,
       col.by = "black",
       leftcols = c("studlab","event","n", "year"),
       leftlabs = c("Country", "Lifetime use (n)", "Total participants (n)", "Data collection (year)"),
       rightcols = c("effect", "ci", "age_range"),
       rightlabs = c("Prevalence", "95% C.I.", "Age, years (range)"),
       xlab = "Prevalence of Lifetime HTP Use", smlab = "", 
       xlim = c(0,20),
       pscale = 100,
       weight.study = "random", squaresize = 0.5, 
       fixed = FALSE,
       digits = 2,
       transf= transf.ipft.hm)
```
##Meta-Regression (age_group): LIFETIME use GENDER WPR
```{r meta-regression_daily: all (Western Pacific Region),echo = FALSE, warning = FALSE, fig.width = 10, fig.height=14}
#all lifetime age_group
ies.dat.all.LT <- escalc(xi = w.cases,
                  ni = total, 
                  data = allbygender_LT_WPR, 
                  keepdata = TRUE,
                  measure = "PFT")

## random-effects model
res <- rma(yi, vi, mods = ~ gender, data=ies.dat.all.LT)
res
```

```{r gender region current, echo = FALSE, warning = FALSE}

allbygender_current_RA<- all %>% 
  filter(timing == "current") %>%
  filter(gender != "all") %>%
  filter(region == "Region of the Americas") %>%
  mutate(prop = round(w.cases/total,3)*100)

allbygender_current_ER<- all %>% 
  filter(timing == "current") %>%
  filter(gender != "all") %>%
  filter(region == "European Region") %>%
  mutate(prop = round(w.cases/total,3)*100)

allbygender_current_WPR<- all %>% 
  filter(timing == "current") %>%
  filter(gender != "all") %>%
  filter(region == "Western Pacific Region") %>%
  mutate(prop = round(w.cases/total,3)*100)
```

##Meta analysis: CURRENT use forest plot GENDER WPR
```{r meta-analysis_current: all (gender),echo = FALSE, warning = FALSE, fig.width = 10, fig.height=14}
# double arcsine transformation
ies.dat.all.gender <- escalc(xi = w.cases,
                  ni = total, 
                  data = allbygender_current_RA, 
                  measure = "PFT")

b.all.gender <- metaprop(event = w.cases, 
            n = total, 
            studlab = country, 
            keepdata = TRUE,
            sm = "PFT", 
            data = ies.dat.all.gender, 
            method = "Inverse", 
            method.tau = "DL", 
            digits = 3,
            subgroup = gender,
            subgroup.name = "Gender")

b.all.gender

forest(b.all.gender,
       col.by = "black",
       leftcols = c("studlab","event","n", "year"),
       leftlabs = c("Country", "Current use (n)", "Total participants (n)", "Data collection (year)"),
       rightcols = c("effect", "ci", "age_range"),
       rightlabs = c("Prevalence", "95% C.I.", "Age, years (range)"),
       xlab = "Prevalence of Current HTP Use", smlab = "", 
       xlim = c(0,20),
       pscale = 100,
       weight.study = "random", squaresize = 0.5, 
       fixed = FALSE,
       digits = 2,
       transf= transf.ipft.hm)
```
```{r gender region daily, echo = FALSE, warning = FALSE}

allbygender_daily_ER<- all %>% 
  filter(timing == "daily") %>%
  filter(gender != "all") %>%
  filter(region == "European Region") %>%
  mutate(prop = round(w.cases/total,3)*100)

allbygender_daily_WPR<- all %>% 
  filter(timing == "daily") %>%
  filter(gender != "all") %>%
  filter(region == "Western Pacific Region") %>%
  mutate(prop = round(w.cases/total,3)*100)
```

##Meta analysis: DAILY use forest plot GENDER WPR
```{r meta-analysis_current: all (gender),echo = FALSE, warning = FALSE, fig.width = 10, fig.height=14}
# double arcsine transformation
ies.dat.all.gender <- escalc(xi = w.cases,
                  ni = total, 
                  data = allbygender_daily_WPR, 
                  measure = "PFT")

b.all.gender <- metaprop(event = w.cases, 
            n = total, 
            studlab = country, 
            keepdata = TRUE,
            sm = "PFT", 
            data = ies.dat.all.gender, 
            method = "Inverse", 
            method.tau = "DL", 
            digits = 3,
            subgroup = gender,
            subgroup.name = "Gender")

b.all.gender

forest(b.all.gender,
       col.by = "black",
       leftcols = c("studlab","event","n", "year"),
       leftlabs = c("Country", "Daily use (n)", "Total participants (n)", "Data collection (year)"),
       rightcols = c("effect", "ci", "age_range"),
       rightlabs = c("Prevalence", "95% C.I.", "Age, years (range)"),
       xlab = "Prevalence of Daily HTP Use", smlab = "", 
       xlim = c(0,20),
       pscale = 100,
       weight.study = "random", squaresize = 0.5, 
       fixed = FALSE,
       digits = 2,
       transf= transf.ipft.hm)
```


##Meta-Regression (age_group): DAILY use GENDER WPR
```{r meta-regression_daily: all (Western Pacific Region),echo = FALSE, warning = FALSE, fig.width = 10, fig.height=14}
#all lifetime age_group
ies.dat.all.LT <- escalc(xi = w.cases,
                  ni = total, 
                  data =allbygender_daily_ER, 
                  keepdata = TRUE,
                  measure = "PFT")

## random-effects model
res <- rma(yi, vi, mods = ~ gender, data=ies.dat.all.LT)
res
```

##Meta-Regression (age_group): LIFETIME use GENDER WPR
```{r meta-regression_daily: all (Western Pacific Region),echo = FALSE, warning = FALSE, fig.width = 10, fig.height=14}
#all lifetime age_group
ies.dat.all.LT <- escalc(xi = w.cases,
                  ni = total, 
                  data = allbygender_LT_WPR, 
                  keepdata = TRUE,
                  measure = "PFT")

## random-effects model
res <- rma(yi, vi, mods = ~ gender, data=ies.dat.all.LT)
res
```