---
title: "metaanalysis_30032022"
author: "Tianze Sun"
date: '2022-03-30'
output: html_document
---

##Setting Up R and Importing Datasets
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#open libarays
library(here)
library(metafor)
library(meta)
library(ggplot2)
library(dplyr)
library(plotly)
library(wesanderson)
library(LaCroixColoR)
library(readxl)

# all surveys combined
all <- read_excel("Updated Datasets/030522_dataset_greylit.xlsx") #all ages
uniquesample <- read_excel("unique samples/unique samples greylit.xlsx") 
```

## Descriptive Statistics
```{r sample size, echo= FALSE, warning=FALSE}
summary(uniquesample)
summary(uniquesample$total)
sum(uniquesample$total)
```

``` {r tables, echo=FALSE, warning=FALSE}
table(all_LT$country)
table(all$country)
table(all$country, all$region)
table(all$author_year)
table(all_LT$country)
table(all_LT$country, all_LT$region)

table(all_current$country)
table(all_current$country, all_current$region)
table(all_current$age_group)


table(all_daily$country)
table(all_daily$country, all_daily$region)

table(all_daily$country, all_daily$region)
table(all$author_year, all$region)

table(all_current$author_year, all_current$region)
table(all_daily$author_year, all_daily$region)
```

##Filtering Variables: by timing among all genders
```{r filter variables,echo = FALSE, warning = FALSE }
## all lifetime
all_LT<- all %>% 
  filter(timing == "lifetime") %>%
  filter(gender == "all") %>%
  mutate(prop = round(w.cases/total,3)*100)

## all current
all_current<- all %>% 
  filter(timing == "current") %>%
  filter(gender == "all") %>%
  mutate(prop = round(w.cases/total,3)*100) 

## all daily
all_daily<- all %>% 
  filter(timing == "daily") %>%
  filter(gender == "all") %>%
  mutate(prop = round(w.cases/total,3)*100) 
```

##Meta analysis: by region among all genders and all age groups for LIFETIME use
```{r meta-analysis_LT: all (region),echo = FALSE, warning = FALSE, fig.width = 10, fig.height=14}
# double arcsine transformation
ies.dat.all.LT <- escalc(xi = w.cases,
                  ni = total, 
                  data = all_LT, 
                  keepdata = TRUE,
                  measure = "PFT")

b.all.LT <- metaprop(event = w.cases, 
            n = total, 
            studlab = country, 
            keepdata = TRUE,
            sm = "PFT", 
            data = ies.dat.all.LT, 
            method = "Inverse", 
            method.tau = "DL", 
            digits = 3,
            subgroup = region,
            subgroup.name = "WHO Region")
b.all.LT

forest(b.all.LT,
       col.by = "black",
       leftcols = c("studlab","author_year", "cohort_abv", "year", "event","n"),
       leftlabs = c("WHO Region and country", "Author (year of publication)", "Cohort", "Data collection (year)", "Lifetime use (n)", "Total participants (n)"),
       rightcols = c("effect", "ci", "age_range", "resentativeness"),
       rightlabs = c("Prevalence", "95% C.I.", "Age, years (range)", "Representativeness"),
       xlab = "Prevalence of Lifetime HTP Use", smlab = "", 
       xlim = c(0,20),
       pscale = 100,
       weight.study = "random", squaresize = 0.5, 
       fixed = FALSE,
       digits = 2,
       transf= transf.ipft.hm)
```

##Meta analysis: by region among all genders and all age groups for CURRENT use
```{r meta-analysis_current: all (region),echo = FALSE, warning = FALSE, fig.width = 10, fig.height=14}
# double arcsine transformation
ies.dat.all.current <- escalc(xi = w.cases,
                  ni = total, 
                  data = all_current, 
                  measure = "PFT")

b.all.current <- metaprop(event = w.cases, 
            n = total, 
            studlab = country, 
            keepdata = TRUE,
            sm = "PFT", 
            data = ies.dat.all.current, 
            method = "Inverse", 
            method.tau = "DL", 
            digits = 3,
            subgroup = region,
            subgroup.name = "WHO Region")
b.all.current

# add Q-test, I^2, and tau^2 estimate info

forest(b.all.current,
       col.by = "black",
       leftcols = c("studlab","author_year", "cohort_abv", "event","n", "year"),
       leftlabs = c("WHO Region and country", "Author (year of publication)", "Cohort", "Current Use (n)", "Total participants (n)", "Data collection (year)"),
       rightcols = c("effect", "ci", "age_range", "resentativeness"),
       rightlabs = c("Prevalence", "95% C.I.", "Age, years (range)", "Representativeness"),
       xlab = "Prevalence of Current HTP use", smlab = "", 
       xlim = c(0,20),
       pscale = 100,
       weight.study = "random", squaresize = 0.5, 
       fixed = FALSE,
       digits = 2,
       transf= transf.ipft.hm)
```

##Meta analysis: by region among all genders and all age groups for DAILY use
```{r meta-analysis_daily: all (region),echo = FALSE, warning = FALSE, fig.width = 10, fig.height=14}
# double arcsine transformation
ies.dat.all.daily <- escalc(xi = w.cases,
                  ni = total, 
                  data = all_daily, 
                  measure = "PFT")

## random-effects model
res <- rma(yi, vi, mods = ~ year, data=ies.dat.all.daily)
res
print(res, digits=3)

b.all.daily <- metaprop(event = w.cases, 
            n = total, 
            studlab = country, 
            keepdata = TRUE,
            sm = "PFT", 
            data = ies.dat.all.daily, 
            method = "Inverse", 
            method.tau = "DL", 
            digits = 3,
            subgroup = region,
            subgroup.name = "WHO Region")

b.all.daily

forest(b.all.daily,
       col.by = "black",
       leftcols = c("studlab","author_year", "cohort_abv", "event","n", "year"),
       leftlabs = c("WHO Region and country", "Author (year of publication)", "Cohort", "Daily use (n)", "Total participants (n)", "Data collection (year)"),
       rightcols = c("effect", "ci", "age_range", "resentativeness"),
       rightlabs = c("Prevalence", "95% C.I.", "Age, years (range)", "Representativeness"),
       xlab = "Prevalence of Daily HTP use", smlab = "", 
       xlim = c(0,20),
       pscale = 100,
       weight.study = "random", squaresize = 0.5, 
       fixed = FALSE,
       digits = 2,
       transf= transf.ipft.hm)
```

###Funnel Plot

```{r funnel plot,echo = FALSE, warning = FALSE }
funnel.meta(b)
metabias(b)
```

##Filtering Variables: by timing among males and females
``` {r gender as moderator, echo = FALSE, warning = FALSE}
## all lifetime gender
allbygender_LT<- all %>% 
  filter(timing == "lifetime") %>%
  filter(gender != "all") %>%
  mutate(prop = round(w.cases/total,3)*100)

## all current gender
allbygender_current<- all %>% 
  filter(timing == "current") %>%
  filter(gender != "all") %>%
  mutate(prop = round(w.cases/total,3)*100) 

## all daily gender
allbygender_daily<- all %>% 
  filter(timing == "daily") %>%
  filter(gender != "all") %>%
  mutate(prop = round(w.cases/total,3)*100) 
```

##Meta analysis: by region among males and females and all age groups for LIFETIME use
```{r meta-analysis_LT: all (gender),echo = FALSE, warning = FALSE, fig.width = 10, fig.height=14}
# double arcsine transformation
ies.dat.all.gender <- escalc(xi = w.cases,
                  ni = total, 
                  data = allbygender_LT, 
                  measure = "PFT")

b.all.gender <- metaprop(event = w.cases, 
            n = total, 
            studlab = country, 
            keepdata = TRUE,
            sm = "PFT", 
            data = ies.dat.all.gender, 
            method = "Inverse", 
            method.tau = "DL", 
            digits = 3,
            subgroup = gender,
            subgroup.name = "Gender")

b.all.gender

forest(b.all.gender,
       col.by = "black",
       leftcols = c("studlab","event","n", "year"),
       leftlabs = c("Country", "Lifetime use (n)", "Total participants (n)", "Data collection (year)"),
       rightcols = c("effect", "ci", "age_range"),
       rightlabs = c("Prevalence", "95% C.I.", "Age, years (range)"),
       xlab = "Prevalence of Lifetime HTP Use", smlab = "", 
       xlim = c(0,20),
       pscale = 100,
       weight.study = "random", squaresize = 0.5, 
       fixed = FALSE,
       digits = 2,
       transf= transf.ipft.hm)
```

##Meta analysis: by region among males and females and all age groups for CURRENT use
```{r meta-analysis_30day: all (gender),echo = FALSE, warning = FALSE, fig.width = 10, fig.height=14}
# double arcsine transformation
ies.dat.all.gender <- escalc(xi = w.cases,
                  ni = total, 
                  data = allbygender_current, 
                  measure = "PFT")

b.all.gender <- metaprop(event = w.cases, 
            n = total, 
            studlab = country, 
            keepdata = TRUE,
            sm = "PFT", 
            data = ies.dat.all.gender, 
            method = "Inverse", 
            method.tau = "DL", 
            digits = 3,
            subgroup = gender,
            subgroup.name = "Gender")

b.all.gender

forest(b.all.gender,
       col.by = "black",
       leftcols = c("studlab","event","n", "year"),
       leftlabs = c("Country", "Current Use (n)", "Total participants (n)", "Data collection (year)"),
       rightcols = c("effect", "ci", "age_range"),
       rightlabs = c("Prevalence", "95% C.I.", "Age, years (range)"),
       xlab = "Prevalence of Current HTP Use", smlab = "", 
       xlim = c(0,20),
       pscale = 100,
       weight.study = "random", squaresize = 0.5, 
       fixed = FALSE,
       digits = 2,
       transf= transf.ipft.hm)
```

##Meta analysis: by region among males and females and all age groups for DAILY use
```{r meta-analysis_daily: all (gender),echo = FALSE, warning = FALSE, fig.width = 10, fig.height=14}
# double arcsine transformation
ies.dat.all.gender <- escalc(xi = w.cases,
                  ni = total, 
                  data = allbygender_daily, 
                  measure = "PFT")

b.all.gender <- metaprop(event = w.cases, 
            n = total, 
            studlab = country, 
            keepdata = TRUE,
            sm = "PFT", 
            data = ies.dat.all.gender, 
            method = "Inverse", 
            method.tau = "DL", 
            digits = 3,
            subgroup = gender,
            subgroup.name = "Gender")

b.all.gender

forest(b.all.gender,
       col.by = "black",
       leftcols = c("studlab","event","n", "year"),
       leftlabs = c("Country", "Daily (n)", "Total participants (n)", "Data collection (year)"),
       rightcols = c("effect", "ci", "age_range"),
       rightlabs = c("Prevalence", "95% C.I.", "Age, years (range)"),
       xlab = "Prevalence of HTP Daily Use", smlab = "", 
       xlim = c(0,20),
       pscale = 100,
       weight.study = "random", squaresize = 0.5, 
       fixed = FALSE,
       digits = 2,
       transf= transf.ipft.hm)
```

##PLOTTING meta analysis: by region across females and males and all age groups for LIFETIME use
```{r plot by gender and region over year,echo = FALSE, warning = FALSE,fig.width = 12, fig.height=4 }
group_all_LT<- all %>% 
  filter(gender == "female"| gender == "male") %>%
  filter(timing == "lifetime") %>%
  mutate(prop = round(w.cases/total,3)*100)

p<- ggplot(group_all_LT, aes(x = factor(year), y = prop)) +
  geom_point(aes(color = gender, shape = gender, alpha=0.5), size = 3.5) +
  scale_colour_manual(values = lacroix_palette("PeachPear", n=2)) +
  xlab("Survey year") +
  ylab("Weighted %") +
  scale_y_continuous(limits = c(0, 10)) + 
    theme(legend.title = element_blank()) +
  theme(axis.text=element_text(size=10),text = element_text(size=12))+
  theme(legend.position="bottom") +
  facet_wrap(~ region)
ggplotly(p)

facet_wrap(~ gender)
```

##PLOTTING meta analysis: by region across females and males and all age groups for LIFETIME use
```{r plot by region over year,echo = FALSE, warning = FALSE,fig.width = 12, fig.height=4 }
group_all_LT<- all %>% 
  filter(timing == "lifetime") %>%
  filter(gender == "all") %>%
  mutate(prop = round(w.cases/total,3)*100)

p<- ggplot(group_all_LT, aes(x = factor(year), y = prop)) +
  geom_point(aes(color = gender, shape = gender, alpha=0.5), size = 3.5) +
  scale_colour_manual(values = lacroix_palette("PeachPear", n=2)) +
  xlab("Survey year") +
  ylab("Weighted %") +
  scale_y_continuous(limits = c(0, 10)) + 
    theme(legend.title = element_blank()) +
  theme(axis.text=element_text(size=10),text = element_text(size=12))+
  theme(legend.position="bottom") +
  facet_wrap(~ region)
ggplotly(p)

facet_wrap(~ gender)
```

##Filtering Variables: by timing among adolescents and adults
```{r age group, echo = FALSE, warning = FALSE,fig.width = 12, fig.height=4 }
## all lifetime age_group
allbyage_LT <- all %>%
  filter(timing == "lifetime") %>%
  filter(age_group != "mixed") %>%
  mutate(prop = round(w.cases/total,3)*100) 

## all current age_group
allbyage_current <- all %>%
  filter(timing == "current") %>%
  filter(age_group != "mixed") %>%
  mutate(prop = round(w.cases/total,3)*100) 

## all daily age_group
allbyage_daily <- all %>%
  filter(timing == "daily") %>%
  filter(age_group != "mixed") %>%
  mutate(prop = round(w.cases/total,3)*100) 
```

##Meta analysis: by region among adolescents and adults and all genders for LIFETIME use
```{r meta-analysis_LT: all (age_group),echo = FALSE, warning = FALSE, fig.width = 10, fig.height=14}
# double arcsine transformation
ies.dat.all.age <- escalc(xi = w.cases,
                  ni = total, 
                  data = allbyage_LT, 
                  measure = "PFT")

b.all.age.LT <- metaprop(event = w.cases, 
            n = total, 
            studlab = country, 
            keepdata = TRUE,
            sm = "PFT", 
            data = ies.dat.all.age, 
            method = "Inverse", 
            method.tau = "DL", 
            digits = 3,
            subgroup = age_group,
            subgroup.name = "Age Group")

b.all.age.LT

forest(b.all.age.LT,
       col.by = "black",
       leftcols = c("studlab","event","n", "year"),
       leftlabs = c("Country", "Lifetime use (n)", "Total participants (n)", "Data collection (year)"),
       rightcols = c("effect", "ci", "age_range"),
       rightlabs = c("Prevalence", "95% C.I.", "Age, years (range)"),
       xlab = "Prevalence of HTP Lifetime Use", smlab = "", 
       xlim = c(0,20),
       pscale = 100,
       weight.study = "random", squaresize = 0.5, 
       fixed = FALSE,
       digits = 3,
       transf= transf.ipft.hm)
```

##Meta analysis: by region among adolescents and adults and all genders for CURRENT use
```{r meta-analysis_current: all (age_group),echo = FALSE, warning = FALSE, fig.width = 10, fig.height=14}
# double arcsine transformation
ies.dat.all.age <- escalc(xi = w.cases,
                  ni = total, 
                  data = allbyage_current, 
                  measure = "PFT")

b.all.age.current <- metaprop(event = w.cases, 
            n = total, 
            studlab = country, 
            keepdata = TRUE,
            sm = "PFT", 
            data = ies.dat.all.age, 
            method = "Inverse", 
            method.tau = "DL", 
            digits = 3,
            subgroup = age_group,
            subgroup.name = "Age Group")

b.all.age.current

forest(b.all.age.current,
       col.by = "black",
       leftcols = c("studlab","event","n", "year"),
       leftlabs = c("Country", "Current Use (n)", "Total participants (n)", "Data collection (year)"),
       rightcols = c("effect", "ci", "age_range"),
       rightlabs = c("Prevalence", "95% C.I.", "Age, years (range)"),
       xlab = "Prevalence of Current HTP use", smlab = "", 
       xlim = c(0,20),
       pscale = 100,
       weight.study = "random", squaresize = 0.5, 
       fixed = FALSE,
       digits = 3,
       transf= transf.ipft.hm)
```

##Meta analysis: by region among adolescents and adults and all genders for DAILY use
```{r meta-analysis_daily: all (age_group),echo = FALSE, warning = FALSE, fig.width = 10, fig.height=14}
# double arcsine transformation
ies.dat.all.age <- escalc(xi = w.cases,
                  ni = total, 
                  data = allbyage_daily, 
                  measure = "PFT")

b.all.age.daily <- metaprop(event = w.cases, 
            n = total, 
            studlab = country, 
            keepdata = TRUE,
            sm = "PFT", 
            data = ies.dat.all.age, 
            method = "Inverse", 
            method.tau = "DL", 
            digits = 3,
            subgroup = age_group,
            subgroup.name = "Age Group")

b.all.age.daily

forest(b.all.age.daily,
       col.by = "black",
       leftcols = c("studlab","event","n", "year"),
       leftlabs = c("Country", "Daily Use (n)", "Total participants (n)", "Data collection (year)"),
       rightcols = c("effect", "ci", "age_range"),
       rightlabs = c("Prevalence", "95% C.I.", "Age, years (range)"),
       xlab = "Prevalence of daily HTP use", smlab = "", 
       xlim = c(0,20),
       pscale = 100,
       weight.study = "random", squaresize = 0.5, 
       fixed = FALSE,
       digits = 3,
       transf= transf.ipft.hm)
```