---
title: "Meta-Regression"
author: "Tianze Sun"
date: '2022-03-29'
output: html_document
---

##Setting Up R and Importing Datasets
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#open libarays
library(here)
library(metafor)
library(meta)
library(ggplot2)
library(dplyr)
library(plotly)
library(wesanderson)
library(LaCroixColoR)
library(dplyr)
library(readxl)

# all surveys combined
all <- read_excel("Updated Datasets/030522_dataset_greylit.xlsx")
alldaily <- read_excel("Updated Datasets/030522_dataset_greylit_dailyplot.xlsx")
uniquesample <- read_excel("unique samples/unique samples greylit.xlsx") 
```

## Descriptive Statistics
``` {r tables, echo=FALSE, warning=FALSE}
table(all_LT$year)
class(all_LT$year)
```

##Filtering Variables: by REGION and LIFETIME use among all genders for adolescents and adults
```{r filter variables,echo = FALSE, warning = FALSE }
## all lifetime Region of the Americas
all_LT_RA<- fixed_data %>% 
  filter(timing == "lifetime") %>%
  filter(gender == "all") %>%
  filter(fixed != "1") %>%
  filter(region == "Region of the Americas") %>%
  mutate(prop = round(w.cases/total,3)*100)

## all lifetime European Region
all_LT_ER<- fixed_data %>% 
  filter(timing == "lifetime") %>%
  filter(gender == "all") %>%
  filter(region == "European Region") %>%
  filter(fixed != "1") %>%
  mutate(prop = round(w.cases/total,3)*100)
  
## all lifetime Western Pacific Region
all_LT_WPR<- fixed_data %>% 
  filter(timing == "lifetime") %>%
  filter(gender == "all") %>%
  filter(fixed != "1") %>%
  filter(region == "Western Pacific Region") %>%
  mutate(prop = round(w.cases/total,3)*100)
```

##Meta-Regression (year): by Region of the Americas and LIFETIME use among all genders and all age groups
```{r meta-analysis_LT: all (Region of the Americas),echo = FALSE, warning = FALSE, fig.width = 10, fig.height=14}
#region of the americas LT
ies.dat.all.LT.RA <- escalc(xi = w.cases,
                  ni = total, 
                  data = all_LT_RA, 
                  keepdata = TRUE,
                  measure = "PFT")

## random-effects model
res <- rma(yi, vi, mods = ~ year, data=ies.dat.all.LT.RA)
summary(res)
```

##Meta-Regression (year): by European Region and LIFETIME use among all genders and all age groups
```{r meta-analysis_LT: all (European Region),echo = FALSE, warning = FALSE, fig.width = 10, fig.height=14}
#European Region LT
ies.dat.all.LT.ER <- escalc(xi = w.cases,
                  ni = total, 
                  data = all_LT_ER, 
                  keepdata = TRUE,
                  measure = "PFT")

## random-effects model
res <- rma(yi, vi, mods = ~ year, data=ies.dat.all.LT.ER)
res
```

##Meta-Regression (year): by Western Pacific Region and LIFETIME use among all genders and all age groups
```{r meta-analysis_LT: all (Western Pacfic),echo = FALSE, warning = FALSE, fig.width = 10, fig.height=14}
#Western Pacific Region LT
ies.dat.all.LT.WPR <- escalc(xi = w.cases,
                  ni = total, 
                  data = all_LT_WPR, 
                  keepdata = TRUE,
                  measure = "PFT")

## random-effects model
res <- rma(yi, vi, mods = ~ year, data=ies.dat.all.LT.WPR)
res
```

##Filtering Variables: by REGION and current among all genders for all age groups
```{r filter variables current,echo = FALSE, warning = FALSE }
## all current Region of the Americas
all_current_RA<- fixed_data %>% 
  filter(timing == "current") %>%
  filter(gender == "all") %>%
  filter(fixed != "1") %>%
  filter(region == "Region of the Americas") %>%
  mutate(prop = round(w.cases/total,3)*100)

## all lifetime European Region
all_current_ER<- fixed_data %>% 
  filter(timing == "current") %>%
  filter(gender == "all") %>%
  filter(fixed != "1") %>%
  filter(region == "European Region") %>%
  mutate(prop = round(w.cases/total,3)*100)
  
## all lifetime Western Pacific Region
all_current_WPR<- fixed_data %>% 
  filter(timing == "current") %>%
  filter(gender == "all") %>%
  filter(fixed != "1") %>%
  filter(region == "Western Pacific Region") %>%
  mutate(prop = round(w.cases/total,3)*100)
```

##Meta-Regression (year): by Region of the Americas and current use among all genders and all age groups
```{r meta-regression_current: all (Region of the Americas),echo = FALSE, warning = FALSE, fig.width = 10, fig.height=14}
#region of the americas LT
ies.dat.all.current.RA <- escalc(xi = w.cases,
                  ni = total, 
                  data = all_current_RA, 
                  keepdata = TRUE,
                  measure = "PFT")

## random-effects model
res <- rma(yi, vi, mods = ~ year, data=ies.dat.all.current.RA)
res
```

##Meta-Regression (year): by European Region and current use among all genders and all age groups
```{r meta-regression_current: all (European Region),echo = FALSE, warning = FALSE, fig.width = 10, fig.height=14}
#European Region LT
ies.dat.all.current.ER <- escalc(xi = w.cases,
                  ni = total, 
                  data = all_current_ER, 
                  keepdata = TRUE,
                  measure = "PFT")

## random-effects model
res <- rma(yi, vi, mods = ~ year, data=ies.dat.all.current.ER)
res
```

##Meta-Regression (year): by Western Pacific Region and current use among all genders and all age groups
```{r meta-regression_current: all (Western Pacific Region),echo = FALSE, warning = FALSE, fig.width = 10, fig.height=14}
#Western Pacific Region LT
ies.dat.all.current.WPR <- escalc(xi = w.cases,
                  ni = total, 
                  data = all_current_WPR, 
                  keepdata = TRUE,
                  measure = "PFT")

## random-effects model
res <- rma(yi, vi, mods = ~ year, data=ies.dat.all.current.WPR)
res
```

##Filtering Variables: by REGION and DAILY use among all genders for all age groups
```{r filter variables daily,echo = FALSE, warning = FALSE }
## all lifetime European Region
all_daily_ER<- all %>% 
  filter(timing == "daily") %>%
  filter(gender == "all") %>%
  filter(region == "European Region") %>%
  mutate(prop = round(w.cases/total,3)*100)
  
## all lifetime Western Pacific Region
all_daily_WPR<- all %>% 
  filter(timing == "daily") %>%
  filter(gender == "all") %>%
  filter(region == "Western Pacific Region") %>%
  mutate(prop = round(w.cases/total,3)*100)
```

##Meta-Regression (year): by European Region and DAILY use among all genders and all age groups
```{r meta-regression_daily: all (European Region),echo = FALSE, warning = FALSE, fig.width = 10, fig.height=14}
#European Region LT
ies.dat.all.daily.ER <- escalc(xi = w.cases,
                  ni = total, 
                  data = all_daily_ER, 
                  keepdata = TRUE,
                  measure = "PFT")

## random-effects model
res <- rma(yi, vi, mods = ~ year, data=ies.dat.all.daily.ER)
res
```

##Meta-Regression (year): by Western Pacific Region and DAILY use among all genders and all age groups
```{r meta-regression_daily: all (Western Pacific Region),echo = FALSE, warning = FALSE, fig.width = 10, fig.height=14}
#Western Pacific Region LT
ies.dat.all.daily.WPR <- escalc(xi = w.cases,
                  ni = total, 
                  data = all_daily_WPR, 
                  keepdata = TRUE,
                  measure = "PFT")

## random-effects model
res <- rma(yi, vi, mods = ~ year, data=ies.dat.all.daily.WPR)
res
```


```{r plot by region over year for lifetime,echo = FALSE, warning = FALSE,fig.width = 12, fig.height=4 }
group_all_LT<- alldaily %>% 
  filter(timing == "lifetime") %>%
  filter(gender == "all") %>%
  filter(region == "European Region" | region == "Region of the Americas" | region == "Western Pacific Region") %>%
  mutate(prop = round(w.cases/total,3)*100)

p<- ggplot(group_all_LT, aes(x = factor(year), y = prop)) +
  geom_point(aes(color = region, shape = region, alpha=0.5), size = 3) +
  scale_colour_manual(values = c("#00AFBB", "#E7B800", "#FC4E07")) +
  scale_fill_manual(values = c("#00AFBB", "#E7B800", "#FC4E07")) +
  xlab("Survey Year") +
  ylab("Weighted Lifetime %") +
  scale_y_continuous(limits = c(0, 15)) + 
  theme(axis.text.x = element_text(angle = 22)) +
  theme(legend.title = element_blank()) +
  theme(axis.text=element_text(size=10),text = element_text(size=12))+
  theme(legend.position = "none") +
  facet_wrap(~ region)
ggplotly(p)
```

```{r plot by region over year for current,echo = FALSE, warning = FALSE,fig.width = 12, fig.height=4 }
group_all_current<- alldaily %>% 
  filter(timing == "current") %>%
  filter(gender == "all") %>%
  filter(region == "European Region" | region == "Region of the Americas" | region == "Western Pacific Region") %>%
  mutate(prop = round(w.cases/total,3)*100)

o<- ggplot(group_all_current, aes(x = factor(year), y = prop)) +
  geom_point(aes(color = region, shape = region, alpha=0.5), size = 3) +
  scale_colour_manual(values = c("#00AFBB", "#E7B800", "#FC4E07")) +
  scale_fill_manual(values = c("#00AFBB", "#E7B800", "#FC4E07")) +
  xlab("Survey Year") +
  ylab("Weighted Current Use %") +
  scale_y_continuous(limits = c(0, 15)) + 
  theme(axis.text.x = element_text(angle = 20)) +
  theme(legend.title = element_blank()) +
  theme(axis.text=element_text(size=10),text = element_text(size=12))+
  theme(legend.position = "none") +
  facet_wrap(~ region)

ggplotly(o)
```

```{r plot by region over year for DAILY,echo = FALSE, warning = FALSE,fig.width = 12, fig.height=4 }
group_all_daily<- alldaily %>% 
  filter(timing == "daily") %>%
  filter(gender == "all") %>%
  filter(region == "European Region" | region == "Region of the Americas" | region == "Western Pacific Region") %>%
  mutate(prop = round(w.cases/total,3)*100)

p<- ggplot(group_all_daily, aes(x = factor(year), y = prop)) +
  geom_point(aes(color = region, shape = region, alpha=0.5), size = 3) +
  scale_colour_manual(values = c("#00AFBB", "#E7B800", "#FC4E07")) +
  scale_fill_manual(values = c("#00AFBB", "#E7B800", "#FC4E07")) +
  xlab("Survey Year") +
  ylab("Weighted Daily %") +
  scale_y_continuous(limits = c(0, 15)) + 
  theme(axis.text.x = element_text(angle = 20)) +
  theme(legend.title = element_blank()) +
  theme(axis.text=element_text(size=10),text = element_text(size=12))+
  theme(legend.position = "none") +
  facet_wrap(~ region)
ggplotly(p)
```

##Filtering Variables: by timing among all genders for adolescents and adults
```{r filter variables,echo = FALSE, warning = FALSE }
## all lifetime age_group
allbyage_LT <- fixed_data %>%
  filter(timing == "lifetime") %>%
  filter(age_group != "mixed") %>%
  filter(fixed != "1") %>%
  mutate(prop = round(w.cases/total,3)*100) 

## all current age_group
allbyage_current <- fixed_data %>%
  filter(timing == "current") %>%
  filter(age_group != "mixed") %>%
  filter(fixed != "1") %>%
  mutate(prop = round(w.cases/total,3)*100) 

## all daily age_group
allbyage_daily <- all %>%
  filter(timing == "daily") %>%
  filter(age_group != "mixed") %>%
  mutate(prop = round(w.cases/total,3)*100) 
```

##Meta-Regression (age_group): by all regions and LIFETIME use among all genders and ADOLESCENTS VS ADULTS
```{r meta-regression_daily: all (Western Pacific Region),echo = FALSE, warning = FALSE, fig.width = 10, fig.height=14}
#all lifetime age_group
ies.dat.all.LT <- escalc(xi = w.cases,
                  ni = total, 
                  data = allbyage_LT, 
                  keepdata = TRUE,
                  measure = "PFT")

## random-effects model
res <- rma(yi, vi, mods = ~ age_group, data=ies.dat.all.LT)
res
```
##Meta-Regression (age_group): by all regions and CURRENT use among all genders and ADOLESCENTS VS ADULTS
```{r meta-regression_daily: all (Western Pacific Region),echo = FALSE, warning = FALSE, fig.width = 10, fig.height=14}
#all lifetime age_group
ies.dat.all.current <- escalc(xi = w.cases,
                  ni = total, 
                  data = allbyage_current, 
                  keepdata = TRUE,
                  measure = "PFT")

## random-effects model
res <- rma(yi, vi, mods = ~ age_group, data=ies.dat.all.current)
res
```

##Filtering Variables: by timing among MALES vs FEMALES for all age groups
```{r filter variables,echo = FALSE, warning = FALSE }
## all lifetime gender
allbygender_LT <- fixed_data %>%
  filter(timing == "lifetime") %>%
  filter(gender != "all") %>%
  filter(fixed != "1") %>%
  mutate(prop = round(w.cases/total,3)*100) 

## all current gender
allbygender_current <- all %>%
  filter(timing == "current") %>%
  filter(gender != "all") %>%
  mutate(prop = round(w.cases/total,3)*100) 

## all daily gender
allbygender_daily <- all %>%
  filter(timing == "daily") %>%
  filter(gender != "all") %>%
  mutate(prop = round(w.cases/total,3)*100) 
```

##Meta-Regression (age_group): by all regions and LIFETIME use among all genders and ADOLESCENTS VS ADULTS
```{r meta-regression_daily: all (Western Pacific Region),echo = FALSE, warning = FALSE, fig.width = 10, fig.height=14}
#all lifetime age_group
ies.dat.all.LT <- escalc(xi = w.cases,
                  ni = total, 
                  data = allbygender_LT, 
                  keepdata = TRUE,
                  measure = "PFT")

## random-effects model
res <- rma(yi, vi, mods = ~ gender, data=ies.dat.all.LT)
res
```

##Filtering Variables: by timing among all genders
```{r filter variables,echo = FALSE, warning = FALSE }
## all lifetime
all_LT<- all %>% 
  filter(timing == "lifetime") %>%
  filter(gender == "all") %>%
  mutate(prop = round(w.cases/total,3)*100)

## all current
all_current<- all %>% 
  filter(timing == "current") %>%
  filter(gender == "all") %>%
  mutate(prop = round(w.cases/total,3)*100) 

## all daily
all_daily<- all %>% 
  filter(timing == "daily") %>%
  filter(gender == "all") %>%
  mutate(prop = round(w.cases/total,3)*100) 
```

##Meta-Regression: by all regions and CURRENT use among all genders and all age groups
```{r meta-regression_current: all,echo = FALSE, warning = FALSE, fig.width = 10, fig.height=14}
#all lifetime age_group
ies.dat.all.current <- escalc(xi = w.cases,
                  ni = total, 
                  data = all_current, 
                  keepdata = TRUE,
                  measure = "PFT")

## random-effects model
res <- rma(yi, vi, mods = ~ year, data=ies.dat.all.current)
res
```

##Meta-Regression: by all regions and LIFETIME use among all genders and all age groups
```{r meta-regression_lifetime: all,echo = FALSE, warning = FALSE, fig.width = 10, fig.height=14}
#all lifetime age_group
ies.dat.all.LT <- escalc(xi = w.cases,
                  ni = total, 
                  data = all_LT, 
                  keepdata = TRUE,
                  measure = "PFT")

## random-effects model
res <- rma(yi, vi, mods = ~ year, data=ies.dat.all.LT)
res
```

##Meta-Regression: by all regions and DAILY use among all genders and all age groups
```{r meta-regression_daily: all,echo = FALSE, warning = FALSE, fig.width = 10, fig.height=14}
#all lifetime age_group
ies.dat.all.daily <- escalc(xi = w.cases,
                  ni = total, 
                  data = all_daily, 
                  keepdata = TRUE,
                  measure = "PFT")

## random-effects model
res <- rma(yi, vi, mods = ~ year, data=ies.dat.all.daily)
res
```